### 2013-12-19 paper/main.tex
cleaned up Control Law, Intuitive Design section
General cleanup of the wording for the Control Law,
Intuitive Design section.  And removed some old
disabled sections.

\caption{Control Law regulator system.
In typical designs a negative feedback is produced using a negative $K$.}
\label{fig:clid01}
\end{figure}
% }}}

A Control Law Design\autocite[Pg. 280]{franklin1998digital} configured
as a regulator is shown in Figure \ref{fig:clid01}.
Notice that there is no input causing it regulate at a constant set point.
However there are several requirements that must be met in order
for this system to be stable.
First the input to $G(z)$ must reflect the output without any offset.
And second the system will always stabilize at zero.

These requirements can be verified intuitively.
Suppose for an input of $1$ to $G(z)$ and output of $5$ is produced.
What value of $K$ will produce a stable value?

@@

An increase in the output creates positive feedback which increases
the input and causes the system diverge.
This exercise can be repeated with a controller that has no offset at zero.
The result is a negative feedback system that will stabilize at zero.

The linear engine model with zero torque (Equation \ref{eq:lems})
supports none of these requirements for a stable Control Law regulator.
The input does not reflect the output; the input range is from zero to
one whereas the output range is from 200 to 1200.
And operation at zero rpm is not realistic.

% {{{ fig:clid02
\begin{figure}[hpb!]
\begin{center}

@@

\caption{Compensations added to the linear engine model with zero
torque ($G(z)$) to construct a regulator system.
The transfer function $R$ converts rpm input to control output (0 - 1).
The rpm input is the desired idle speed such as 700.
Notice that both the output ($y$) and input ($u$) will be zero when
the desired rpm is reached.}
\label{fig:clid02}
\end{figure}
% }}}

The system in Figure \ref{fig:clid02} adds compensations to the
engine model so that a regulator system can be constructed.
Figure \ref{fig:cl_plot1} shows the response of this system.
While the response isn't very good the design was trivial
by simply choosing an arbitrary constant of $0.01$ for $K$.
Later designs will improve performance by elaborating upon this
system and developing more complex values for $K$.

% {{{ fig:dd_plot2
\begin{figure}[htbp!]
\begin{center}
\includegraphics[scale=0.6]{../octave/cl_ff01}
\end{center}
\caption{Output response of Control Law regulator with $K = 0.01$
and rpm = $700$.
Rpm was allowed to stabilize at 200 rpm before applying a step
to 700 rpm.
Source code is provided in Appendix \ref{app:cl_matlab}.}
\label{fig:cl_plot1}
\end{figure}
% }}}

%Instead of a servo system, which accepts a control input,
%a regulator system can be constructed which tries to maintain
%a single output value.  The general design is shown
%in Figure \ref{fig:reg1}.

% {{{ fig:reg1, Regulator System
%\begin{figure}[hbp!]
%\begin{center}
%
%\begin{tikzpicture}[>=triangle 60, scale=0.8,
%	node distance=14mm, auto]
%
%	\node[gain] 	(engine)	[]					{engine};
%	\node[gain] 	(control)	[below=of engine]	{controller};
%
%	\draw [<-] (engine.north) -- ++(0,10mm) node[above]{$\text{torque}$};
%	\draw [->] (engine.east) node[above,xshift=7mm]{rpm}
%					-- ++(20mm,0)
%					|- (control.east);
%	\draw [->] (control.west)
%					-- ++(-20mm,0)
%					|- (engine.west) node[above,xshift=-9mm]{control};
%\end{tikzpicture}
%
%\end{center}
%\caption{Regulator system for idle rpm control.}\label{fig:reg1}
%\end{figure}
% }}}

%One way to build this regulator system is to use the
%Control Law Design\autocite[Pg. 280]{franklin1998digital}.
%The block diagram of the system is shown in Figure \ref{fig:clff1}.

% {{{ fig:clff1
%\begin{figure}[hpb!]
%\begin{center}
%
%\begin{tikzpicture}[>=triangle 60,
%	node distance=14mm, auto]
%
%	\node[gain]  	(Gz)	[] 	{$\begin{matrix}
%									\dot{x} = Ax + Bu \\
%										 y = Cx + Du
%								 \end{matrix}$};
%	\node[gain] 	(K)	[below=of Gz] 	{$-K$};
%
%	 \draw [->]
%	 		(Gz.east) -- ++(15mm,0)
%			-| ++(0,-10mm)
%			|- (K.east);
%
%	 \draw [<-]
%	 		(Gz.west) -- ++(-15mm,0)
%			-| ++(0,-10mm)
%			|- (K.west);
%
%\end{tikzpicture}
%
%\end{center}
%
%\caption{Control Law system with full feedback.
%It behaves as a regulator since not input is available.}
%\label{fig:clff1}
%\end{figure}
% }}}

>>>>

\caption{Control Law regulator system.
Typically, $-K$ is used to create negative feedback.}
\label{fig:clid01}
\end{figure}
% }}}

A Control Law Design\autocite[Pg. 280]{franklin1998digital} configured
as a regulator is shown in Figure \ref{fig:clid01}.
Notice that there is no input which means it acts as a regulator as
opposed to a servo.

There are several requirements that must be met in order for this
system to be stable.
First, the input to $G(z)$ must reflect the output without any offset.
And second the system must stabilize at zero.
These requirements can be verified intuitively.
Suppose for an input of $1$ to $G(z)$ an output of $5$ is produced.
What value of $K$ will produce a stable value?

@@

An increase in the output creates positive feedback which increases
the input causing a further increase in the output.
The system diverges.
This exercise can be repeated with a controller that has no offset at zero.
The result is a negative feedback system that will stabilize at zero.

The linear engine model with zero torque (Equation \ref{eq:lems})
satisfies neither of these requirements.
The input does not reflect the output; the input range is from zero to
one whereas the output range is from 200 to 1200.
And operation at zero rpm is not realistic.

% {{{ fig:clid02
\begin{figure}[!htp]
\begin{center}

@@

\caption{Compensations added to the linear engine model with zero
torque ($G(z)$) to construct a regulator system.
The transfer function $R$ converts rpm input to control output (0 - 1).
The rpm input is the desired idle speed (e.g. 700).
Notice that both the output ($y$) and input ($u$) will be zero when
the desired rpm is reached.}
\label{fig:clid02}
\end{figure}
% }}}

The system in Figure \ref{fig:clid02} adds compensations to the
engine model so that a regulator system can be constructed.
An input of zero should produce the desired rpm.
And this rpm input is converted to a control value ($R$).
And the reached rpm (output of $G(z)$) is subtracted from
the goal rpm to produce a zero output.

% {{{ fig:cl_plot1
\begin{figure}[!htp]
\begin{center}
\includegraphics[scale=0.6]{../octave/cl_ff01}
\end{center}
\caption{Output response of Control Law regulator with $K = 0.01$
and rpm = $700$.
Rpm was allowed to stabilize at 200 rpm before applying a step
to 700 rpm.
Source code is provided in Appendix \ref{app:cl_matlab}.}
\label{fig:cl_plot1}
\end{figure}
% }}}

Figure \ref{fig:cl_plot1} shows the response of this system.
While the response isn't very good the design was trivial.
A value for $K$ was arbitrarily chosen.
Any values less than one were stable and larger values diverged.
Later designs will improve performance by elaborating upon this
system and developing more complex values for $K$.
